Supplementary Material for Asymmetry paper

### 2020-05-15 Supplementary/Sup_mat.Rmd
supmat updated

@@

## Experiment 2: Two Throws
```{r load in model for two throws, include = F, echo = F}
load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos")
load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos_draws")
```

@@

## Experiment 3: Reward
```{r load in gambling data, include = F, echo = F, warning = F}
load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri")
load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri_draws")
draws_df <- draws_df %>% 
  mutate(prop = boot::inv.logit(estimate))

>>>>

``` {r prob matching power, include = F, echo = F, cache = T}
load("../power/Prob_match/scratch/df_resample")

# sampling
n_trials <- 300 # seq(100, 450, 50)
n_subs <- seq(2, 20, 1)
n_iter <- 5000
conditions <- unique(df_resample$Condition)

# setup data.table 
n <- length(n_subs) * length(conditions) * n_iter
df_sample <- data.table::data.table(iter = rep(0, n),
                                    n_sub = rep(0, n),
                                    n_trials = rep(0, n),
                                    Condition = rep("", n),
                                    Most = rep(0, n))

# run loop
counter <- 0
for(ii in 1:n_iter){
  # loop conditions
  for(cond in conditions){
    ss_cond <- df_resample %>%
      filter(Condition == cond)

    # loop n trials
    for(trials in n_trials){
      # loop n subjects
      for(sub in n_subs){
        # get random participants
        subj <- sample(ss_cond$Participant, sub, replace = T)

        # get data
        ss_sub <- ss_cond %>%
          filter(Participant %in% subj)

        # set this for a stopping point
        # final_sub <- tail(unique(ss_sub$Participant), n = 1)

        # initialise vector
        samp <- c()

        # loop through participants
        count <- 0
        for(unique_sub in subj){
          count <- count + 1
          # who are we sampling from?
          sampling <- ss_sub %>%
            filter(Participant == unique_sub)

          # sample random trials
          samp <- c(samp, sample(sampling$Most, trials, replace = T))

          # check if we're adding this to the data frame
          if(count == length(subj)){
            counter <- counter + 1
            df_sample[counter, iter := ii]
            df_sample[counter, n_sub := sub]
            df_sample[counter, n_trials := trials]
            df_sample[counter, Condition := cond]
            df_sample[counter, Most := mean(samp)]
          }
        }
      }
    }
  }
}

@@

## Experiment 2: Two Throws
```{r load in model for two throws, include = F, echo = F}
# load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos")
# load("../Analyses/Experiment_2_Two_throw/modelling/model_outputs/m1_pos_draws")
```

```{r Two-throws modelling, include = F, echo = F, cache = T}
load("../Analyses/Experiment_2_Two_throw/scratch/model_data_pos")

source("extract_draws_functions/Two_throw_draws.R")

Two_throw_m1 <- brm(abspos ~ norm_delta * Num_throws + (norm_delta * Num_throws|Participant),
                    family = "beta",
                    data = model_data_pos,
                    prior = c(set_prior("student_t(3,0,3)", class = "b")),
                    cores = 1,
                    chains = 1,
                    iter = 2000,
                    warmup = 1000)

draws <- draw_post_delta(Two_throw_m1, model_data_pos)

@@

## Experiment 3: Reward
```{r load in gambling data, include = F, echo = F, warning = F, cache=T}
# load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri")
# load("../Analyses/Experiment_5_Unequal_Reward/scratch/model_outputs/m_brms_ri_draws")
load("../Analyses/Experiment_5_Unequal_Reward/scratch/data/model_data")

source("extract_draws_functions/Reward_draws.R")

# run model 
Reward_m1 <- brm(Norm_Dist ~ dist_type*Gamble_Type + (dist_type*Gamble_Type|Participant),
                 data = model_data,
                 family = "beta",
                 chains = 1,
                 iter = 4000,
                 warmup = 2000)

draws_df <- draws_factor(Reward_m1) %>% 
  mutate(prop = boot::inv.logit(estimate))
